\LARGE{{\bf{Piled up gravitational waves:} \\ \bf{Searching for new signals of $N$naturalness} }}

### 2019-08-01 gwnnDraft02.tex
fixing typos

Using these restrictions, we can examine the behaviour of standard sectors with a much larger vev than our own. In terms of the $N$naturalness framework, this consisted of looking at various different sectors above the critical index, as mentioned in Sec. \ref{sec:dQCD}. The signals for both the maximal case ($10^{16}$ limit) and several other high transition temperatures (involving sectors $i > 10^{10}$) scenarios are show in Sec. \ref{sec:signals}.

>>>>

Using these restrictions, we can examine the behaviour of standard sectors with a much larger vev than our own. In terms of the $N$naturalness framework, this consisted of looking at various different sectors above the critical index, as mentioned in Sec. \ref{sec:dQCD}. The signals for both the maximal case ($10^{16}$ limit) and several other high transition temperatures (involving sectors $i > 10^{10}$) scenarios are shown in Sec. \ref{sec:signals}.
